---
title: "Meta Regression Executive Control, Attention, Intelligence, Motor Learning and Motor Memory"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r warning=TRUE, include=FALSE}
library("tidyverse")
library("metafor")
library("robumeta")
library("readxl")
library("writexl")
```

```{r data download, include=FALSE}

directory = "/Users/shreygrover/Desktop/MetaAnalysis_SciTranslMed/Sci_Transl_Med_Submission_2/Analysis/Scripts_Revised/Meta_Datafiles_2021"
mlm.data <- read_excel(paste0(directory, "/Data_for_analysis/Analysis_Outcome_Revised.xlsx"))

# test w/o clinical studies
#mlm.data <- mlm.data[mlm.data$population != "Clinical",]

```

```{r new variables and subsetting, include=FALSE}

# set to 1 to exclude outliers from the analysis, 0 otherwise
out_exclude = 1

# assigning montage category
mlm.data["montage_cat"] <- 'anterior'
mlm.data[mlm.data$montage == 'Parietal' | mlm.data$montage == 'Occipital' | mlm.data$montage == 'Temporal',"montage_cat"] <- 'posterior'
mlm.data[mlm.data$montage == 'Fronto-Parietal' | mlm.data$montage == 'Fronto-Occipital' | mlm.data$montage == 'Fronto-Temporal',"montage_cat"]<- 'anterior-posterior'

# intensity as a dichotomous variable
mlm.data$intensity_cat <- factor(ifelse(mlm.data$intensity>1, "high", "low"))

# creating lateralization variable
mlm.data$lateral <- factor(ifelse(mlm.data$lateralization == 'Bilateral', "bilateral", "unilateral"))

# age as a dichotomous variable
mlm.data$age <- factor(ifelse(mlm.data$mean_age>50, "elderly", "young"))

# creating design variable
mlm.data$design <- factor(ifelse(mlm.data$n == mlm.data$n1, "within", "between"))

# converting frequency to a numeric variable
mlm.data$freq_num <- as.numeric(mlm.data$freq_num)

# converting current density to a numeric variable
mlm.data$current_density <- as.numeric(mlm.data$current_density)

# performance and reaction time subsets of data 
mlm.perf <- mlm.data[mlm.data$dv == 'Performance',]
mlm.rt <- mlm.data[mlm.data$dv == 'RT',]
```

## Executive Control

```{r, include=FALSE}
mlm.data_domain <- subset(mlm.data, domain == 'Executive Control')
mlm.perf_domain <- subset(mlm.perf, domain == 'Executive Control')
mlm.rt_domain <- subset(mlm.rt, domain == 'Executive Control')
```

*Exclude outliers*

```{r, echo = FALSE}
# All
model_rve<- robu(formula = y ~ 1, data = mlm.data_domain, studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.data_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.data_domain <- mlm.data_domain[! mlm.data_domain$experiment %in% outliers,]
}

# Performance
model_rve<- robu(formula = y ~ 1, data = mlm.perf_domain,studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.perf_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.perf_domain <- mlm.perf_domain[! mlm.perf_domain$experiment %in% outliers,]
}

# RT
model_rve<- robu(formula = y ~ 1, data = mlm.rt_domain,studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.rt_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.rt_domain <- mlm.rt_domain[! mlm.rt_domain$experiment %in% outliers,]
}
```

```{r, include = FALSE}
preds <- colnames(mlm.data_domain)
preds <- preds[-(1:36)]
for(i in 1:length(preds)){
  print(preds[i])
  print(table(mlm.data_domain[,preds[i]]))
  print("------------------------------")
}
```

*OK: freq_num, intensity num, intensity cat, CM, HD, blinding* 

## All 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- robu(formula = y ~ 1 + freq_num, data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.data_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Current Modeling*
**Categorical: no (0), yes (1)**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(current_modeling), data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*HD*
**Categorical: traditional (0), HD (1)**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(HD), data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Blinding*
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(blinding), data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.data_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

## Performance 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- robu(formula = y ~ 1 + freq_num, data=mlm.perf_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- rbind(reg_perf_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.perf_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- rbind(reg_perf_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.perf_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

## RT 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_rt_output <- robu(formula = y ~ 1 + freq_num, data=mlm.rt_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_rt_output <- rbind(reg_rt_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.rt_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```
*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_rt_output <- rbind(reg_rt_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.rt_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

Save files
```{r, include = FALSE}
if(out_exclude == 0) {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_exec.csv"))
  write_csv(reg_perf_output, paste0(directory, "/Results/Regression_OtherDomains/regression_perf_exec.csv"))
  write_csv(reg_rt_output, paste0(directory, "/Results/Regression_OtherDomains/regression_rt_exec.csv"))
}else {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_exec_outremoved.csv"))
  write_csv(reg_perf_output, paste0(directory, "/Results/Regression_OtherDomains/regression_perf_exec_outremoved.csv"))
  write_csv(reg_rt_output, paste0(directory, "/Results/Regression_OtherDomains/regression_rt_exec_outremoved.csv"))
}
```

## Attention 

```{r, include=FALSE}
mlm.data_domain <- subset(mlm.data, domain == 'Attention')
mlm.perf_domain <- subset(mlm.perf, domain == 'Attention')
# not enough effects for RT regression
```

*Exclude outliers*

```{r, echo = FALSE}
# All
model_rve<- robu(formula = y ~ 1, data = mlm.data_domain, studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.data_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.data_domain <- mlm.data_domain[! mlm.data_domain$experiment %in% outliers,]
}

# Performance
model_rve<- robu(formula = y ~ 1, data = mlm.perf_domain,studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.perf_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.perf_domain <- mlm.perf_domain[! mlm.perf_domain$experiment %in% outliers,]
}

```

```{r, include = FALSE}
preds <- colnames(mlm.data_domain)
preds <- preds[-(1:36)]
for(i in 1:length(preds)){
  print(preds[i])
  print(table(mlm.data_domain[,preds[i]]))
  print("------------------------------")
}
```

*OK: freq_num, intensity num, lateralization, design* 

## All 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- robu(formula = y ~ 1 + freq_num, data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.data_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Lateralization*
**Categorical: bilateral, unilateral**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(lateral), data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Design*
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(design), data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.data_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```


## Performance 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- robu(formula = y ~ 1 + freq_num, data=mlm.perf_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- rbind(reg_perf_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.perf_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```
*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- rbind(reg_perf_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.perf_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```
Save files
```{r, include = FALSE}
if(out_exclude == 0) {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_att.csv"))
  write_csv(reg_perf_output, paste0(directory, "/Results/Regression_OtherDomains/regression_perf_att.csv.csv"))
}else {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_att_outremoved.csv"))
  write_csv(reg_perf_output, paste0(directory, "/Results/Regression_OtherDomains/regression_perf_Att_outremoved.csv"))
}
```


## Intelligence 

```{r, include=FALSE}
mlm.data_domain <- subset(mlm.data, domain == 'Intelligence')
mlm.perf_domain <- subset(mlm.perf, domain == 'Intelligence')
# not enough effects for RT regression
```

*Exclude outliers*

```{r, echo = FALSE}
# All
model_rve<- robu(formula = y ~ 1, data = mlm.data_domain, studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.data_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.data_domain <- mlm.data_domain[! mlm.data_domain$experiment %in% outliers,]
}

# Performance
model_rve<- robu(formula = y ~ 1, data = mlm.perf_domain,studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.perf_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.perf_domain <- mlm.perf_domain[! mlm.perf_domain$experiment %in% outliers,]
}

```

## All 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- robu(formula = y ~ 1 + freq_num, data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.data_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```
*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.data_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

## Performance 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- robu(formula = y ~ 1 + freq_num, data=mlm.perf_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- rbind(reg_perf_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.perf_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```
*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_perf_output <- rbind(reg_perf_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.perf_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

Save files
```{r, include = FALSE}
if(out_exclude == 0) {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_int.csv"))
  write_csv(reg_perf_output, paste0(directory, "/Results/Regression_OtherDomains/regression_perf_int.csv"))
}else {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_int_outremoved.csv"))
  write_csv(reg_perf_output, paste0(directory, "//Results/Regression_OtherDomains/regression_perf_int_outremoved.csv"))
}
```

## Motor Learnnig 

```{r, include=FALSE}
mlm.data_domain <- subset(mlm.data, domain == 'Motor Learning')
```

*Exclude outliers*

```{r, echo = FALSE}
# All
model_rve<- robu(formula = y ~ 1, data = mlm.data_domain, studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.data_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.data_domain <- mlm.data_domain[! mlm.data_domain$experiment %in% outliers,]
}

```

```{r, include = FALSE}
preds <- colnames(mlm.data_domain)
preds <- preds[-(1:36)]
for(i in 1:length(preds)){
  print(preds[i])
  print(table(mlm.data_domain[,preds[i]]))
  print("------------------------------")
}
```

*OK: freq_num, intensity num, rs_task* 

## All 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- robu(formula = y ~ 1 + freq_num, data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.data_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Timing of stimulation*
**Categorical: resting state, task**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(rs_task), data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```
*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.data_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

Save files
```{r, include = FALSE}
if(out_exclude == 0) {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_motlearn.csv"))
}else {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_motlearn_outremoved.csv"))
}
```

## Motor Memory 

```{r, include=FALSE}
mlm.data_domain <- subset(mlm.data, domain == 'Motor Memory')
```

*Exclude outliers*

```{r, echo = FALSE}
# All
model_rve<- robu(formula = y ~ 1, data = mlm.data_domain, studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
model_rma <- rma.uni(y, v, weights = model_rve$data.full$r.weights, data=mlm.data_domain)
rstud <- rstudent(model_rma)
outliers <- model_rve$data$experiment[abs(rstud$z) >= 1.96]

if (out_exclude == 1){
  mlm.data_domain <- mlm.data_domain[! mlm.data_domain$experiment %in% outliers,]
}

```

```{r, include = FALSE}
preds <- colnames(mlm.data_domain)
preds <- preds[-(1:36)]
for(i in 1:length(preds)){
  print(preds[i])
  print(table(mlm.data_domain[,preds[i]]))
  print("------------------------------")
}
```

*OK: freq_num, intensity num, intensity cat, duration, lateralization, blinding* 

## All 

*Frequency*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- robu(formula = y ~ 1 + freq_num, data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table
```

*Intensity*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(intensity), data= subset(mlm.data_domain, intensity!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

**Categorical: Low (<= 1 mA), High (>1 mA)**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + intensity_cat, data= subset(mlm.data_domain, intensity_cat!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Duration* 
**Categorical: 0 - <20 min, 1 - > 20 min**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(duration), data= mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Lateralization*
**Categorical: bilateral, unilateral**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(lateral), data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

*Blinding*
**Categorical: single (1), double (2)**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.factor(blinding), data=mlm.data_domain, studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```
*Current Density*
**Continuous**
```{r, echo = FALSE}
reg_all_output <- rbind(reg_all_output, robu(formula = y ~ 1 + as.numeric(current_density), data= subset(mlm.data_domain, current_density!="-"), studynum = ID, v, rho = .8, small = TRUE)$reg_table)
```

Save files
```{r, include = FALSE}
if(out_exclude == 0) {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_motmem.csv"))
}else {
  write_csv(reg_all_output, paste0(directory, "/Results/Regression_OtherDomains/regression_all_motmem_outremoved.csv"))
}
```
