---
title: "&nbsp;"
output:
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
  word_document: default
editor_options:
  chunk_output_type: inline
---

```{r warning=TRUE, include=FALSE}
library("metafor")
library("robumeta")
library("readxl")
library("writexl")
library("plotly")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(dpi=300)
```

```{r data download, include=FALSE}

directory = "/Users/shreygrover/Desktop/MetaAnalysis_SciTranslMed/Sci_Transl_Med_Submission_2/Analysis/Scripts_Revised/Meta_Datafiles_2021"
mlm.data <- read_excel(paste0(directory, "/Data_for_analysis/Analysis_Outcome_Revised.xlsx"))

mlm.perf <- mlm.data[mlm.data$dv == 'Performance',]
mlm.rt <- mlm.data[mlm.data$dv == 'RT',]
mlm.clin <- mlm.data[mlm.data$population == 'Clinical',]
```

*Effects of tACS on All measures by Domains *
```{r effects by domains, include=FALSE}

domains = c("Working Memory", "Long-Term Memory", "Attention", "Executive Control", "Intelligence", "Motor Learning", "Motor Memory")

effects_robu = data.frame(matrix(ncol = 7, nrow = 8))
model = list()

for(d in 1:length(domains)) {
  model[[d]] <- robu(formula = y ~ 1, 
                        data = mlm.data[mlm.data$domain==domains[d],],
                        studynum = ID, 
                        var.eff.size = v, 
                        rho = .8, 
                        small = TRUE)
  effects_robu[d] <- c(model[[d]]$reg_table$b.r,
                       model[[d]]$reg_table$SE,
                       model[[d]]$reg_table$prob,
                       model[[d]]$reg_table$CI.L,
                       model[[d]]$reg_table$CI.U,
                       model[[d]]$mod_info$I.2[1],
                       model[[d]]$reg_table$dfs,
                       length(model[[d]]$data.full$effect.size)
                       )
}

colnames(effects_robu) <- domains
rownames(effects_robu) <- c('es', 'se', 'pval', 'ci_lb', 'ci_up', 'I^2', 'df', 'n')

```

*Outlier removal function*
```{r outlier removal function, include = FALSE}

remove_rst <- function(df, model_domain, domain) {
  # Takes in a data set (All, Performance or RT), an RVE model fitted by robu() function and the name of the
  # cognitive domain and returns an RVE model with domain-specific outliers removed
  
  df <- df[df$domain==domain,]
  model_rma <- rma.uni(y, v, weights = model_domain$data.full$r.weights, data=df)
  rstud <- rstudent(model_rma)
  outliers <- model_domain$data$experiment[abs(rstud$z) >= 1.96]
  if(sum(abs(rstud$z) >= 1.96) !=0) {
    model_out <- robu(formula = y ~ 1, data = df[abs(rstud$z)<1.96,], studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
    return(list(model_out, outliers))
  }else{
    # if no outliers identified, returns the same domain-specific RVE model
    return(list(model_domain, outliers))
  }
}
```

*remove outliers within each domain*
```{r domains All (outlieers removed), echo=FALSE}
effects_robu_out = data.frame(matrix(ncol = 7, nrow = 8))
model_out = list()

for(d in 1:length(domains)) {
  model_out[[d]] <- remove_rst(df = mlm.data, model = model[[d]], domains[d])

  effects_robu_out[d] <- c(model_out[[d]][[1]]$reg_table$b.r,
                       model_out[[d]][[1]]$reg_table$prob,
                       model_out[[d]][[1]]$reg_table$CI.L,
                       model_out[[d]][[1]]$reg_table$CI.U,
                       model_out[[d]][[1]]$mod_info$I.2[1],
                       model_out[[d]][[1]]$reg_table$dfs,
                       model_out[[d]][[1]]$N,
                       model_out[[d]][[1]]$M)
}

colnames(effects_robu_out) <- domains
rownames(effects_robu_out) <- c('es', 'pval', 'ci_lb', 'ci_up', 'I^2', 'df', 'N', 'k')
```

*function to extract data for forest plots*
```{r get_data function, include=FALSE}
# function that gets data from the models
# takes in an RVE model and a scaling factor for plotting. Scaling is applied to the weights of the effects. Each weight determines the size of the effect size marker, scaling can be necessary for better visualization.  

get_data <- function(model, model_out, scale_size = 2) {
  names <- c(model$data$experiment, "Total Effect", "Effect w/o Outliers") # names of experiments
  effects <- c(model$data.full$effect.size, model$reg_table$b.r, model_out$reg_table$b.r) # effect sizes for each experiment and the total effect
  sds <- c(model$data.full$sd.eff.size*1.96, model$reg_table$SE*1.96, model_out$reg_table$SE*1.96) # confidence intervals
  weights <- c(model$data.full$r.weights*scale_size, 9, 9) # weights of effects scaled by a scaling factor 
  
  df <- data.frame(names, effects, sds, weights) # put into a data frame
  return(df)
}
```

*function to make the forest plot*
```{r forest function, include=FALSE}
#Forest plotting function
# takes in data extracted by the get_data() function, domain name, color for plotting, and a boolean for plotting total effect size for the respective domain (default is TRUE)

forest_plotly <- function(data, domain, domain_color = 'rgba(84,39,143, 0.9)', total_effect = TRUE, outs){
  
  data = data
  yorder <- data$names
  yform <- list(categoryorder = "array", categoryarray = yorder)
  
  # symbols for plotting
  if (total_effect){
    es_symbols <- c(rep('square', length(data$names)-2), 'diamond','diamond')
    es_colors <- c(rep(domain_color, length(data$names)-2), '#000000', '#990918')
  } else {
    es_symbols <- c(rep('square', length(data$names)))
    es_colors <- c(rep(domain_color, length(data$names)))
  }
  
  es_colors[outs] = '#990918'
  
  fig <- plot_ly(type='scatter', mode='markers')
  
  for (i in seq_along(data$names)){
    fig <- fig %>% add_markers(
      data = data,
      opacity=0.7,
      x=data$effects[i],
      y=data$names[i], 
      error_x=list(array=data$sds[i], color=es_colors[i]),
      marker=list(color=es_colors[i], size = data$weights[i], line = list(color = es_colors[i], width = 1), symbol = es_symbols[i]),
      showlegend=F
    )
  }
  
  fig <- fig %>% layout(yaxis = list(title = ''), xaxis = list(title = '', range = c(-1.5, 2.5))) 
  fig <- fig %>% layout(yaxis = yform)
  fig <- fig %>% layout(yaxis = list(autorange = 'reversed'))
  fig <- fig %>% layout(font = list(size = 7))
  fig
}
```

*make the forest plots for each domain*
```{r forests_new, warning=FALSE, echo = FALSE, fig.dim=c(8, 12)}

#Forest Plots After Outlier Removal
s1 <- forest_plotly(get_data(model[[1]], model_out[[1]][[1]], 1.5), 'Working Memory', domain_color = 'rgba(84,39,143, 0.9)', total_effect = TRUE, outs <- c(15,37,52,58))
s2 <- forest_plotly(get_data(model[[5]], model_out[[5]][[1]], 0.8), 'Intelligence', domain_color = 'rgba(223,101,176, 0.9)', total_effect = TRUE, outs <- c(2))

fig1 <- subplot(s1, s2, nrows = 2, heights = c(0.8, 0.2), margin = c(0.06, 0.06, 0.02, 0.03)) 

fig1 <- fig1 %>% layout(annotations = list(
  list(x = 0.33 , y = 1.0, text = "Working Memory", showarrow = F, xref='paper', yref='paper', xanchor = "center", 
      yanchor = "bottom", font = list(size = 12)),
  list(x = 0.33 , y = 0.18, text = "Intelligence", showarrow = F, xref='paper', yref='paper', xanchor = "center", 
      yanchor = "bottom", font = list(size = 12)))
)

s3 <- forest_plotly(get_data(model[[2]], model_out[[2]][[1]], 1.4), 'Long-Term Memory', domain_color = 'rgba(29,145,192, 0.9)', total_effect = TRUE, outs <- c(12,44,49,52))
s4 <- forest_plotly(get_data(model[[4]], model_out[[4]][[1]], 2.5), 'Executive Control', domain_color = 'rgba(252,141,89, 0.9)',total_effect = TRUE, outs <- c(14))


fig2 <- subplot(s3, s4, nrows = 2, heights = c(0.7, 0.3), margin = c(0.06, 0.06, 0.02, 0.03))

fig2 <- fig2 %>% layout(annotations = list(
  list(x = 0.33 , y = 1.0, text = "Long-Term Memory", showarrow = F, xref='paper', yref='paper', xanchor = "center", 
      yanchor = "bottom", font = list(size = 12)),
  list(x = 0.33 , y = 0.28, text = "Executive Control", showarrow = F, xref='paper', yref='paper', xanchor = "center", 
      yanchor = "bottom", font = list(size = 12)))
)

s5 <- forest_plotly(get_data(model[[3]], model_out[[3]][[1]]), 'Attention', domain_color = 'rgba(65,171,93, 0.9)', total_effect = TRUE, outs <- c(2))
s6 <- forest_plotly(get_data(model[[6]], model_out[[6]][[1]], 3), 'Motor Learning', domain_color = 'rgba(11,11,69, 0.9)', total_effect = TRUE, outs <-c(1,20,21)) # 227, 26, 28
s7 <- forest_plotly(get_data(model[[7]], model_out[[7]][[1]], 3), 'Motor Memory', domain_color = 'rgba(254,217,118, 0.9)', total_effect = TRUE, outs <- c(2,18))

fig3 <- subplot(s5, s6, s7, nrows = 3, heights = c(0.26, 0.3, 0.44), margin = c(0.06, 0.06, 0.03, 0.03))

fig3 <- fig3 %>% layout(annotations = list(
  list(x = 0.33 , y = 1.0, text = "Attention", showarrow = F, xref='paper', yref='paper', xanchor = "center", 
      yanchor = "bottom", font = list(size = 12)),
  list(x = 0.33 , y = 0.72, text = "Motor Learning", showarrow = F, xref='paper', yref='paper', xanchor = "center", 
      yanchor = "bottom", font = list(size = 12)),
  list(x = 0.33 , y = 0.42, text = "Motor Memory", showarrow = F, xref='paper', yref='paper', xanchor = "center", 
      yanchor = "bottom", font = list(size = 12)))
)

fig <- subplot(fig1, fig2, fig3, nrows = 1, widths = c(0.33,0.33, 0.33), margin = c(0.07, 0.07, 0.02, 0.02))
fig <- fig %>% layout(showlegend = FALSE, width = 9.5*96, height = 8.5*96) # sizing for the web version

htmlwidgets::saveWidget(as_widget(fig), paste0(directory, "/Results/FigureOutputs/ForestPlots.html"))

# different sizing for the print version
fig <- fig %>% layout(showlegend = FALSE, width = 7.2*144, height = 9.7*144)
fig
orca(fig, "/Results/FigureOutputs/ForestPlots.svg",
        width = 7.2*144,
        height = 9.7*144)

```

*Boxplots for each domain before outlier removal*
```{r boxplots domains, warning=FALSE, echo = FALSE}
dom_colors = c('rgba(84,39,143, 0.9)', 'rgba(29,145,192, 0.9)', 'rgba(65,171,93, 0.9)', 'rgba(252,141,89, 0.9)', 'rgba(223,101,176, 0.9)', 'rgba(11,11,69, 0.9)', 'rgba(254,217,118, 0.9)')


fig1 <- plot_ly(y = model_out[[1]][[1]]$data$y, type = "box", boxpoints = "all", name = "WM", jitter = 0.3, pointpos = -1.8, marker = list(color =  'rgba(84,39,143, 0.9)'), line = list(color = 'rgba(84,39,143, 0.9)'), width = 800, height = 400)

fig1 <- fig1 %>% add_trace(y = model[[2]]$data$y, name="LTM", marker = list(color = 'rgba(29,145,192, 0.9)'), line = list(color = 'rgba(29,145,192, 0.9)')) 
fig1 <- fig1 %>% add_trace(y = model[[3]]$data$y, name="Att", marker = list(color = 'rgba(65,171,93, 0.9)'),  line = list(color = 'rgba(65,171,93, 0.9)'))
fig1 <- fig1 %>% add_trace(y = model[[4]]$data$y, name="EC", marker = list(color = 'rgba(252,141,89, 0.9)'),  line = list(color = 'rgba(252,141,89, 0.9)'))
fig1 <- fig1 %>% add_trace(y = model[[5]]$data$y, name="Int", marker = list(color = 'rgba(223,101,176, 0.9)'),  line = list(color = 'rgba(223,101,176, 0.9)'))
fig1 <- fig1 %>% add_trace(y = model[[6]]$data$y, name="ML", marker = list(color = 'rgba(11,11,69, 0.9)'),line = list(color = 'rgba(11,11,69, 0.9)'))
fig1 <- fig1 %>% add_trace(y = model[[7]]$data$y, name="MM", marker = list(color = 'rgba(254,217,118, 0.9)'),  line = list(color = 'rgba(254,217,118, 0.9)'))

fig1 <- fig1 %>% layout(yaxis = list(title = "Hedges' G"),
                        colorway = dom_colors, showlegend = FALSE, 
                        annotations = list(
                        list(x = 0.5 , y = 1.0, text = "Distribution of Effect Sizes by Cognitive Domains Before Outlier Removal",
                        showarrow = F, xref='paper', yref='paper', xanchor = "center", yanchor = "bottom", 
                        font = list(size = 14))))
```

*Point estimates for each domains before outlier removal*
```{r point estimates domains, warning=FALSE, echo = FALSE}

# put domain effects in a data frame
d_effects <- as.data.frame(t(as.matrix(effects_robu)))
d_effects <- round(d_effects, 3)
d_effects$domain <- c("WM", "LTM", "Att", "EC", "Int", "ML", "MM")
rownames(d_effects) <- NULL

xorder <- d_effects$domain
xform <- list(categoryorder = "array", categoryarray = xorder)

fig2 <- plot_ly(type='scatter', mode='markers', width = 800, height = 400)

for (i in seq_along(d_effects$es)){
    fig2 <- fig2 %>% add_markers(
    data = d_effects,
    opacity=0.7,
    x=d_effects$domain[i],
    y=d_effects$es[i], 
    error_y=list(type = "constant", value = d_effects$ci_up[i] - d_effects$es[i],  color=dom_colors[i]),
    marker=list(color=dom_colors[i], line = list(color = dom_colors[i], width = 1), size = 15),
    showlegend=F
  )
}

fig2 <- fig2 %>% layout(yaxis = list(title = "Hedges' G"), xaxis = list(title = ''), title = "")
fig2 <- fig2 %>% layout(xaxis = xform)
fig2 <- fig2 %>% layout(annotations = list(
                        list(x = 0.5 , y = 1.0, text = "Overall Effect Size Estimates by Cognitive Domains Before Outlier Removal",
                        showarrow = F, xref='paper', yref='paper', xanchor = "center", yanchor = "bottom", 
                        font = list(size = 14))))
```

*Combine the boxplot and point estimates to make the domains summary plot*

```{r domains summary, warning=FALSE, warning=FALSE, echo = FALSE}
fig <- subplot(fig1, fig2, nrows = 2, margin = c(0.05, 0.05, 0.02, 0.03), shareX = TRUE, shareY = TRUE)
fig <- fig %>% layout(showlegend = FALSE, yaxis = list(title = "Hedges' G"), width = 7.2*144, height= 6.5*144)

fig

htmlwidgets::saveWidget(as_widget(fig), paste0(directory, "/Results/FigureOutputs/DomainsSummaryBeforeOutLierRemoval.html"))

orca(fig, "/Results/FigureOutputs/DomainsSummaryBeforeOutLierRemoval.svg",
       width = 7.2*144,
       height = 5.9*144)
```


*Boxplots for each domain after outlier removal*
```{r boxplots domains after outlier removal, warning=FALSE, echo = FALSE}
dom_colors = c('rgba(84,39,143, 0.9)', 'rgba(29,145,192, 0.9)', 'rgba(65,171,93, 0.9)', 'rgba(252,141,89, 0.9)', 'rgba(223,101,176, 0.9)', 'rgba(11,11,69, 0.9)', 'rgba(254,217,118, 0.9)')


fig1 <- plot_ly(y = model_out[[1]][[1]]$data$y, type = "box", boxpoints = "all", name = "WM", jitter = 0.3, pointpos = -1.8, marker = list(color =  'rgba(84,39,143, 0.9)'), line = list(color = 'rgba(84,39,143, 0.9)'), width = 800, height = 400)

fig1 <- fig1 %>% add_trace(y = model_out[[2]][[1]]$data$y, name="LTM", marker = list(color = 'rgba(29,145,192, 0.9)'), line = list(color = 'rgba(29,145,192, 0.9)')) 
fig1 <- fig1 %>% add_trace(y = model_out[[3]][[1]]$data$y, name="Att", marker = list(color = 'rgba(65,171,93, 0.9)'),  line = list(color = 'rgba(65,171,93, 0.9)'))
fig1 <- fig1 %>% add_trace(y = model_out[[4]][[1]]$data$y, name="EC", marker = list(color = 'rgba(252,141,89, 0.9)'),  line = list(color = 'rgba(252,141,89, 0.9)'))
fig1 <- fig1 %>% add_trace(y = model_out[[5]][[1]]$data$y, name="Int", marker = list(color = 'rgba(223,101,176, 0.9)'),  line = list(color = 'rgba(223,101,176, 0.9)'))
fig1 <- fig1 %>% add_trace(y = model_out[[6]][[1]]$data$y, name="ML", marker = list(color = 'rgba(11,11,69, 0.9)'),line = list(color = 'rgba(11,11,69, 0.9)'))
fig1 <- fig1 %>% add_trace(y = model_out[[7]][[1]]$data$y, name="MM", marker = list(color = 'rgba(254,217,118, 0.9)'),  line = list(color = 'rgba(254,217,118, 0.9)'))

fig1 <- fig1 %>% layout(yaxis = list(title = "Hedges' G"),
                        colorway = dom_colors, showlegend = FALSE, 
                        annotations = list(
                        list(x = 0.5 , y = 1.0, text = "Distribution of Effect Sizes by Cognitive Domains After Outlier Removal",
                        showarrow = F, xref='paper', yref='paper', xanchor = "center", yanchor = "bottom", 
                        font = list(size = 14))))
```

*Point estimates for each domains after outlier removal*
```{r point estimates domains after outlier removal, warning=FALSE, echo = FALSE}

# put domain effects in a data frame
d_effects <- as.data.frame(t(as.matrix(effects_robu_out)))
d_effects <- round(d_effects, 3)
d_effects$domain <- c("WM", "LTM", "Att", "EC", "Int", "ML", "MM")
rownames(d_effects) <- NULL

xorder <- d_effects$domain
xform <- list(categoryorder = "array", categoryarray = xorder)

fig2 <- plot_ly(type='scatter', mode='markers', width = 800, height = 400)

for (i in seq_along(d_effects$es)){
    fig2 <- fig2 %>% add_markers(
    data = d_effects,
    opacity=0.7,
    x=d_effects$domain[i],
    y=d_effects$es[i], 
    error_y=list(type = "constant", value = d_effects$ci_up[i] - d_effects$es[i],  color=dom_colors[i]),
    marker=list(color=dom_colors[i], line = list(color = dom_colors[i], width = 1), size = 15),
    showlegend=F
  )
}

fig2 <- fig2 %>% layout(yaxis = list(title = "Hedges' G"), xaxis = list(title = ''), title = "")
fig2 <- fig2 %>% layout(xaxis = xform)
fig2 <- fig2 %>% layout(annotations = list(
                        list(x = 0.5 , y = 1.0, text = "Overall Effect Size Estimates by Cognitive Domains After Outlier Removal",
                        showarrow = F, xref='paper', yref='paper', xanchor = "center", yanchor = "bottom", 
                        font = list(size = 14))))
```

*Combine the boxplot and point estimates to make the domains summary plot after outlier removal*

```{r domains summary aftr outlier removal, warning=FALSE, warning=FALSE, echo = FALSE}
fig <- subplot(fig1, fig2, nrows = 2, margin = c(0.05, 0.05, 0.02, 0.03), shareX = TRUE, shareY = TRUE)
fig <- fig %>% layout(showlegend = FALSE, yaxis = list(title = "Hedges' G"), width = 7.2*144, height= 6.5*144)

fig

htmlwidgets::saveWidget(as_widget(fig), paste0(directory, "/Results/FigureOutputs/DomainsSummaryAfterOutLierRemoval.html"))

orca(fig, "/Results/FigureOutputs/DomainsSummaryAfterOutLierRemoval.svg",
       width = 7.2*144,
       height = 5.9*144)
```


*Results Summary Boxplots*
```{r boxplots results, warning=FALSE}
fig_colors = c('rgba(136,65,157, 0.9)', 'rgba(128,125,186, 0.9)', 'rgba(128,125,186, 0.9)','rgba(67,147,195, 0.9)','rgba(252,146,114, 0.9)','rgba(146,197,222, 0.9)','rgba(33,102,172, 0.9)','rgba(244,165,130, 0.9)','rgba(214,96,77, 0.9)','rgba(1,108,89, 0.9)','rgba(2,129,138, 0.9)') 

# all effects, perf, RT
sp1 <- plot_ly(y = mlm.data$y, type = "box", boxpoints = "all", name = "All", jitter = 0.3, pointpos = -1.8, marker = list(color =  fig_colors[1]), line = list(color = fig_colors[1]))
sp1 <- sp1 %>% add_trace(y = mlm.perf$y, name="Perf", marker = list(color =  fig_colors[12]), line = list(color = fig_colors[2]))
sp1 <- sp1 %>% add_trace(y = mlm.rt$y, name="RT", marker = list(color =  fig_colors[3]), line = list(color = fig_colors[3]))
sp1 <- sp1 %>% layout(yaxis = list(range = c(-1.5, 2)))

# offline vs online perf
sp2 <- plot_ly(y = mlm.perf[mlm.perf$online == 0,]$y, type = "box", boxpoints = "all", name="Offline", jitter = 0.3, pointpos = -1.8, marker = list(color =  fig_colors[4]), line = list(color = fig_colors[4]))
sp2 <- sp2 %>% add_trace(y = mlm.perf[mlm.perf$online == 1,]$y, name="Online", marker = list(color =  fig_colors[5]), line = list(color = fig_colors[5]))
sp2 <- sp2 %>% layout(yaxis = list(range = c(-1.5, 2)))

# offline * current modeling interaction
sp3 <- plot_ly(y = mlm.perf[mlm.perf$online == 0 & mlm.perf$current_modeling == 0,]$y, type = "box", boxpoints = "all", name="Off w/o CM", jitter = 0.3, pointpos = -1.8, marker = list(color =  fig_colors[6]), line = list(color = fig_colors[6]))
sp3 <- sp3 %>% add_trace(y = mlm.perf[mlm.perf$online == 0 & mlm.perf$current_modeling == 1,]$y, name="Off + CM", marker = list(color =  fig_colors[7]), line = list(color = fig_colors[7]))
sp3 <- sp3 %>% add_trace(y = mlm.perf[mlm.perf$online == 1 & mlm.perf$current_modeling == 0,]$y, name="On w/o CM", marker = list(color =  fig_colors[8]), line = list(color = fig_colors[8]))
sp3 <- sp3 %>% add_trace(y = mlm.perf[mlm.perf$online == 1 & mlm.perf$current_modeling == 1,]$y, name="On + CM", marker = list(color =  fig_colors[9]), line = list(color = fig_colors[9]))

# phase 
mlm.data_ph <- read_excel(paste0(directory, "/Data_for_analysis/Analysis_Hypothesis_Revised.xlsx"))
# select only studies with intentional phase manipulation
mlm.data_ph <- mlm.data_ph[mlm.data_ph$phase_intent == 1,]
# changes signs for anti-phase effects 
mlm.data_ph[mlm.data_ph$phase == 2,]$y <- mlm.data_ph[mlm.data_ph$phase == 2,]$y*(-1)

sp4 <- plot_ly(y = mlm.data_ph[mlm.data_ph$hypothesis == 1 & mlm.data_ph$phase == 1,]$y, type = "box", boxpoints = "all", name="In-Phase Improvement", jitter = 0.3, pointpos = -1.8, marker = list(color =  fig_colors[10]), line = list(color = fig_colors[10]))

sp4 <- sp4 %>% add_trace(y = mlm.data_ph[mlm.data_ph$hypothesis == 2 & mlm.data_ph$phase == 2,]$y, name="Anti-Phase Impairment", marker = list(color =  fig_colors[11]), line = list(color = fig_colors[11]))

sp4 <- sp4 %>% layout(colorway = fig_colors)

fig3 <- subplot(sp1, sp2, sp3, sp4, nrows = 1, widths = c(0.25,0.175, 0.4, 0.175), margin = c(0.03, 0.03, 0.02, 0.02), shareY=T)

fig3 <- fig3 %>% layout(yaxis = list(title = "Hedges' G", range = c(-1.5, 2)),
                      xaxis = list(showticklabels=FALSE),
                      xaxis2 = list(showticklabels=FALSE),
                      xaxis3 = list(showticklabels=FALSE),
                      xaxis4 = list(showticklabels=FALSE),
                      colorway = fig_colors, showlegend = FALSE, 
                      annotations = list(
                      list(x = 0.5 , y = 1.0, text = "Distribution of Effect Sizes",
                      showarrow = F, xref='paper', yref='paper', xanchor = "center", yanchor = "bottom", 
                      font = list(size = 14))))


fig3 <- fig3 %>% layout(width = 7.2*144,
                      height = 5.9/2*144) 
fig3
```

```{r point estimates data, warning=FALSE}
# point estimates and CIs of effect sizes for plotting
summary_effects <- data.frame("es" = c(0.289, 0.3, 0.186, 0.385, 0.180, 0.321, 0.591, 0.301, 0.035, 0.317, -0.314),"ci_lb"= c(0.212, 0.213, 0.063, 0.265, 0.064, 0.195, 0.295, 0.134, -0.113, 0.103, -0.546), "ci_up" = c(0.365, 0.386, 0.308, 0.506, 0.297, 0.446, 0.887,0.469, 0.182, 0.531, -0.082), "name" = c("Overall", "Perf", "RT", "Offline", "Online", "Off w/o CM", "Off + CM", "On w/o CM", "On + CM ", "In-phase", "Anti-phase"))

```

*Results Summary Point Estimates*
```{r point estimates plot, warning=FALSE}
xorder <- summary_effects$name
xform <- list(categoryorder = "array", categoryarray = xorder[1:3])

sp21 <- plot_ly(type='scatter', mode='markers')
for (i in 1:3){
    sp21 <- sp21 %>% add_markers(
    data = summary_effects,
    opacity=0.7,
    x=summary_effects$name[i],
    y=summary_effects$es[i], 
    error_y=list(type = "constant", value = summary_effects$ci_up[i] - summary_effects$es[i],  color=fig_colors[i]),
    marker=list(color=fig_colors[i], line = list(color = fig_colors[i], width = 1), size = 15),
    showlegend=F
  )
}
sp21 <- sp21 %>% layout(xaxis = xform)


xform <- list(categoryorder = "array", categoryarray = xorder[4:5])
sp22 <- plot_ly(type='scatter', mode='markers')

for (i in 4:5){
    sp22 <- sp22 %>% add_markers(
    data = summary_effects,
    opacity=0.7,
    x=summary_effects$name[i],
    y=summary_effects$es[i], 
    error_y=list(type = "constant", value = summary_effects$ci_up[i] - summary_effects$es[i],  color=fig_colors[i]),
    marker=list(color=fig_colors[i], line = list(color = fig_colors[i], width = 1), size = 15),
    showlegend=F
  )
}
sp22 <- sp22 %>% layout(xaxis = xform)


xform <- list(categoryorder = "array", categoryarray = xorder[6:9])
sp23 <- plot_ly(type='scatter', mode='markers')

for (i in 6:9){
    sp23 <- sp23 %>% add_markers(
    data = summary_effects,
    opacity=0.7,
    x=summary_effects$name[i],
    y=summary_effects$es[i], 
    error_y=list(type = "constant", value = summary_effects$ci_up[i] - summary_effects$es[i],  color=fig_colors[i]),
    marker=list(color=fig_colors[i], line = list(color = fig_colors[i], width = 1), size = 15),
    showlegend=F
  )
}
sp23 <- sp23 %>% layout(xaxis = xform)


xform <- list(categoryorder = "array", categoryarray = xorder[10:11])
sp24 <- plot_ly(type='scatter', mode='markers')

for (i in 10:11){
    sp24 <- sp24 %>% add_markers(
    data = summary_effects,
    opacity=0.7,
    x=summary_effects$name[i],
    y=summary_effects$es[i], 
    error_y=list(type = "constant", value = summary_effects$ci_up[i] - summary_effects$es[i],  color=fig_colors[i]),
    marker=list(color=fig_colors[i], line = list(color = fig_colors[i], width = 1), size = 15),
    showlegend=F
  )
}
sp24 <- sp24 %>% layout(xaxis = xform)

fig4 <- subplot(sp21, sp22, sp23, sp24, nrows = 1, widths = c(0.25,0.175, 0.4, 0.175), margin = c(0.03, 0.03, 0.02, 0.02), shareY = TRUE)


fig4 <- fig4 %>% layout(yaxis = list(title = "Hedges' G"),
                        colorway = fig_colors, showlegend = FALSE, 
                        annotations = list(
                        list(x = 0.5 , y = 1.0, text = "Effects Size estimates",
                        showarrow = F, xref='paper', yref='paper', xanchor = "center", yanchor = "bottom", 
                        font = list(size = 14))))


fig4 <- fig4 %>% layout(width = 7.2*144,
                      height = 5.9/2*144)

```


```{r results summary plot, warning=FALSE}
fig <- subplot(fig3, fig4, nrows = 2, margin = c(0.03, 0.03, 0.02, 0.03), shareY = TRUE) 
fig <- fig %>% layout(showlegend = FALSE, yaxis = list(title = "Hedges' G"))
fig <- fig %>% layout(width = 7.2*144,
                      height = 5.9*144)
fig

htmlwidgets::saveWidget(as_widget(fig), paste0(directory, "/Results/FigureOutputs/SummaryPlot.html"))
 
save_image(fig, paste0(directory, "/Results/FigureOutputs/SummaryPlot.svg"),width = 7.2*144, height = 5.9*144)
```


*FIGURE 8*

*Subplot1: Older adults, All measures, All experiments, Outliers marked, Forest Plot*
```{r older adults forest, echo=FALSE, fig.dim=c(8, 12), warning=FALSE}

# RVE model for older adults
model_elderly <- robu(formula = y ~ 1, data= subset(mlm.data, population=="elderly", ), studynum = ID, 
                        var.eff.size = v, rho = .8, small = TRUE)

# RVE model for older adults after removing outliers
model_rma <- rma.uni(y, v, weights = model_elderly$data.full$r.weights, data=subset(mlm.data, population=="elderly"))
rstud <- rstudent(model_rma)
outliers_elderly <- model_elderly$data$experiment[abs(rstud$z) >= 1.96]
model_elderly_out <- robu(formula = y ~ 1, data= subset(mlm.data, population=="elderly" & !experiment %in% outliers_elderly), studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
print(outliers_elderly)
# Outliers identified: "Paßmann (2016) 1a" "Rumpf (2019) 1a". Indices: 17, 24.

# subplot 1
fig5 <- forest_plotly(get_data(model_elderly, model_elderly_out, 2.5), '', domain_color = 'rgba(2,56,88, 0.9)', total_effect = TRUE,  outs <- c(17, 24)) # outs location manually entered after checking locations of the outliers in the output of the get_data function

fig5 <- fig5 %>% layout(annotations = list(x = 0.43 , y = 1.0, text = "Older Adults", showarrow = F, xref='paper',
                                         yref='paper', xanchor = "center", 
                                         yanchor = "bottom", font = list(size = 12)),
                                         xaxis = list(title = '', range = c(-1.5, 2)),
                                         width = 300,
                                         height = 600) 
```

*Subplot 2a: Older adults, All measures, Boxplot before outlier removal, Boxplot after outlier removal*
```{r older adults boxplot, warning = FALSE, echo =FALSEFALSE}

fig6 <- plot_ly(y = mlm.data[mlm.data$population == "elderly",]$y, type = "box", boxpoints = "all", name = "Before OR", jitter = 0, pointpos = -1.8, marker = list(color =  'rgba(2,56,88, 0.9)'), line = list(color = 'rgba(2,56,88, 0.9)'), width = 300, height = 300)

fig6 <- fig6 %>% layout(yaxis = list(title = "Hedges' G", range=c(-0.6, 1.7)),
                        colorway = 'rgba(2,56,88, 0.9)', showlegend = FALSE)

fig6 <- fig6 %>% add_trace(y = model_elderly_out$data$y, name = "After OR", marker = list(color =  'rgba(2,56,88, 0.9)'), line = list(color = 'rgba(2,56,88, 0.9)'))
```

*Subplot 2b: Older adults, All measures, Point estimates before and after outlier removal*
```{r older adults point estimate, warning = FALSE, echo = FALSE}

older_effect <- data.frame("es" = c(round(model_elderly$reg_table$b.r,3), round(model_elderly_out$reg_table$b.r,3)), "ci_up" = c(round(model_elderly$reg_table$CI.U, 3), round(model_elderly_out$reg_table$CI.U,3)), "name" = c("Before OR", "After OR"))

fig7 <- plot_ly(type='scatter', mode='markers', width = 300, height = 300)

fig7 <- fig7 %>% add_markers(opacity=0.7, 
x= c(0.25, 0.75),
y=older_effect$es, 
error_y=list(type = "data" , array = array(older_effect$ci_up - older_effect$es),  color='rgba(2,56,88, 0.9)'),
marker=list(color='rgba(2,56,88, 0.9)', line = list(color = 'rgba(2,56,88, 0.9)', width = 1), size = 15),
showlegend=F)

fig7 <- fig7 %>% layout(yaxis = list(title = "Hedges' G", range = c(-0.2, 1.5)), xaxis = list(title = '', range = c(0,1), tickvals = c(0.25, 0.75), ticktext = older_effect$name), title = " ")
```

*Subplot 2: Older adults, All measures, combining boxplots and point estimates before and after outlier removal*
```{r older adults summary plot, warning=FALSE, echo=FALSE}
# boxplot and point estimate
fig8 <- subplot(fig6, fig7, nrows = 2, margin = c(0.03, 0.03, 0.02, 0.03), shareY = TRUE)
fig8 <- fig8 %>% layout(showlegend = FALSE, yaxis = list(title = "Hedges' G"))
fig8 <- fig8 %>% layout(width = 300,
                      height = 600)
fig8
```

*Subplot 3: Clinical populations, All functional outcomes, Outliers identified, Forest plot* 
```{r clinical functional outcomes, warning=FALSE, echo=FALSE}

# RVE model for all functional outcomes in clinical studies
model_clin_cog<- robu(formula = y ~ 1, data = subset(mlm.clin, dv != "clinical score"), studynum = ID, var.eff.size = v, rho = .8, small = TRUE)

# RVE model after removing outliers
model_rma <- rma.uni(y, v, weights = model_clin_cog$data.full$r.weights, data = subset(mlm.clin, dv != "clinical score"))
rstud <- rstudent(model_rma)
outliers_clin <- model_clin_cog$data$experiment[abs(rstud$z) >= 1.96]
model_clin_cog_out <- robu(formula = y ~ 1, data= subset(mlm.clin, dv != "clinical score" & !experiment %in% outliers_clin), studynum = ID, var.eff.size = v, rho = .8, small = TRUE)

print(outliers_clin)
# outliers identified: "Del Felice (2015) 1b" "Ladenbauer (2017) 1b", Location: 9, 24 checked in the output of the get_data function

fig10 <- forest_plotly(get_data(model_clin_cog, model_clin_cog_out, 2.5), '', domain_color = 'rgba(82,56,88, 0.9)', total_effect = TRUE,  outs <- c(9, 24))

fig10 <- fig10 %>% layout(annotations = list(x = 0.43 , y = 1.0, text = "Clinical populations", showarrow = F, xref='paper',
                                         yref='paper', xanchor = "center", 
                                         yanchor = "bottom", font = list(size = 12)),
                                         xaxis = list(title = '', range = c(-1.5, 2)),
                                         width = 300,
                                         height = 600) 
```

*Subplot 4a: Clinical populations, All functional outcomes, Boxplot before and after outlier removal*
```{r clinical populations boxplot, warning = FALSE, echo =FALSEFALSE}

fig11 <- plot_ly(y = model_clin_cog$data$y, type = "box", boxpoints = "all", name = "Before OR", jitter = 0, pointpos = -1.8, marker = list(color =  'rgba(82,56,88, 0.9)'), line = list(color = 'rgba(82,56,88, 0.9)'), width = 300, height = 300)

fig11 <- fig11 %>% layout(yaxis = list(title = "Hedges' G", range=c(-0.6, 1.7)),
                        colorway = 'rgba(82,56,88, 0.9)', showlegend = FALSE)

fig11 <- fig11 %>% add_trace(y = model_clin_cog_out$data$y, name = "After OR", marker = list(color =  'rgba(82,56,88, 0.9)'), line = list(color = 'rgba(82,56,88, 0.9)'))

```

*Subplot 4b: Clinical populations, All functional outcomes, Point estimates before and after outlier removal*
```{r clinical populations point estimate, warning = FALSE, echo = FALSE}

clinical_effect <- data.frame("es" = c(round(model_clin_cog$reg_table$b.r,3), round(model_clin_cog_out$reg_table$b.r,3)), "ci_up" = c(round(model_clin_cog$reg_table$CI.U, 3), round(model_clin_cog_out$reg_table$CI.U,3)), "name" = c("Before OR", "After OR"))

fig12 <- plot_ly(type='scatter', mode='markers', width = 300, height = 300)

fig12 <- fig12 %>% add_markers(opacity=0.7, 
x= c(0.25, 0.75),
y=clinical_effect$es, 
error_y=list(type = "data" , array = array(clinical_effect$ci_up - clinical_effect$es),  color='rgba(82,56,88, 0.9)'),
marker=list(color='rgba(82,56,88, 0.9)', line = list(color = 'rgba(82,56,88, 0.9)', width = 1), size = 15),
showlegend=F)

fig12 <- fig12 %>% layout(yaxis = list(title = "Hedges' G", range = c(-0.2, 1.5)), xaxis = list(title = '', range = c(0,1), tickvals = c(0.25, 0.75), ticktext = clinical_effect$name), title = " ")
```

*Subplot 4: Clinical populations, All functional outcomes, combining boxplots and point estimates before and after outlier removal*
```{r clinical adults summary plot, warning=FALSE, echo=FALSE}
# boxplot and point estimate
fig13 <- subplot(fig11, fig12, nrows = 2, margin = c(0.03, 0.03, 0.02, 0.03), shareY = TRUE) 
fig13 <- fig13 %>% layout(showlegend = FALSE, yaxis = list(title = "Hedges' G"))
fig13 <- fig13 %>% layout(width = 300,
                      height = 600)
fig13
```

*Figure8: Combining forest plots, boxplot and point estimates for older adults and clinical populations into one figure*
```{r older and clinical populations final summary plot, warning = FALSE, echo = FALSE}
# final subplot including forest plot
#fig14 <- subplot(fig5, fig8, fig10, fig13, nrows = 1, margin = c(0.01,0.08,0.02,0.002), shareY = TRUE)
#fig14 <- fig14 %>% layout(width = 1200,height = 600)

fig15 <- subplot(fig5, fig8, fig10, nrows = 1, margin = c(0.01,0.08,0.02), shareY = TRUE)
fig15 <- fig15 %>% layout(width = 1200,
                          height = 600)
fig15

#htmlwidgets::saveWidget(as_widget(fig14), paste0(directory, "/Results/FigureOutputs/SummaryOlderClinical.html"))

#orca(fig14, "/Results/FigureOutputs/SummaryOlderClinical.svg", width = 1200, height = 600)

```